\section{Problem formulation}

\subsection{Framework}

Let
$\givenFamily \subset \probabilitiesOver{\R}$ 
be a given famility of distributions on the line. 
The subset $\givenFamily$ is assumed to be a 
convex subset of $\probabilitiesOver{\R}$.
Let
$t$ 
denote a generic distribution in the given family $\givenFamily$.

Let
$\familiyDistribution$ 
be a probability over the $\givenFamily$. 

Let
$\statisticsSpace$ 
be a separable metric space.

Let
$\statistics: \givenFamily \rightarrow \statisticsSpace$ 
be a measurable map, 
interpreted as some statistics over the given family $\givenFamily$.

Let 
$\pushforwardStat = \statistics_{\#} \familiyDistribution$
be the pushforward of $\familiyDistribution$ via $\statistics$,
namely 
$\pushforwardStat$ is the probability measure on $\statisticsSpace$
such that for any measurable $A \subset \statisticsSpace$ 
it holds
$\pushforwardStat(A) = \familiyDistribution (\statistics\inverse(A))$.


We fix a non-negative continuous cost function
$c:\R \times \statisticsSpace \mapsto \R$.
For every $t$ in $\givenFamily$,
we define the $c$-optimal coupling between 
$t$ and $\pushforwardStat$ by the formula
\begin{equation}
\label{eq.definition_of_t_coupling}
\coupling[t] = 
\argmin 
\left\lbrace
	\int_{\R \times \statisticsSpace}
	c(u, x)\nu(du, dx):
\nu \in \probabilitiesOver{\R\times \statisticsSpace},
\nu(\cdot, \statisticsSpace) = t,
\nu(\R, \cdot) = \pushforwardStat
\right\rbrace.
\end{equation}

Is $\coupling[t]$ well-defined? 
I.e. what are the assumptions such that the map 
$
\nu\mapsto \int c(u, x) \nu(du, dx)
$
achieves a minimiser over the set of 
$
\nu \in \probabilitiesOver{\R\times \statisticsSpace}
$
with
$
\nu(\cdot, \statisticsSpace) = t
$
and 
$
\nu(\R, \cdot) = \pushforwardStat
$
?
Is this minimiser unique?


\subsection{The baricentre problem}

Let $\bariDistance$ be a distance over 
$\probabilitiesOver{\R\times\statisticsSpace}$.
We would like to study the minimisation of
\begin{equation}
\label{eq.baricentre_minimisation}
F: 
\baricentre 
\mapsto
\int_{\givenFamily} \bariDistance(\coupling[t], \baricentre) \familiyDistribution(dt),
\,\,\,
\baricentre \in \probabilitiesOver{\R\times\statisticsSpace},
\end{equation}
where
$\coupling[t]$, 
for $t$ in $\givenFamily$, 
is as in equation \eqref{eq.definition_of_t_coupling}.

Is the infimum
$\inf\lbrace F(\baricentre): \, \baricentre \in \probabilitiesOver{\R\times\statisticsSpace}\rbrace$
achieved?
If it is, we call any minimiser of $F$ the 
$\familiyDistribution$-baricentre.

If existent, is the $\familiyDistribution$-baricentre unique?

If $\baricentre$ is a $\familiyDistribution$-baricentre,
does it hold that
$
\baricentre(\R, \cdot) = \pushforwardStat
$
?
Let 
$\mathcal{P}_{\pushforwardStat}$
be the space
of 
$\baricentre$ in 
$\probabilitiesOver{\R\times\statisticsSpace}$ 
such that 
$
\baricentre(\R, \cdot) = \pushforwardStat
$
?
Can we restrict  $F$ to $\mathcal{P}_{\pushforwardStat}$ 
and
study the minimisation of $F$ over $\mathcal{P}_{\pushforwardStat}$? 
In other words, can we study the following inequality?
\begin{equation*}
\inf
\lbrace 
F(\baricentre): \, 
\baricentre \in \probabilitiesOver{\R\times\statisticsSpace}
\rbrace
\,\,\,
\leq
\,\,\,
\inf
\lbrace 
F(\baricentre): \, 
\baricentre \in \mathcal{P}_{\pushforwardStat}
\rbrace
.
\end{equation*}


We would like to interpret any 
$\familiyDistribution$-baricentre 
$\baricentre$
as follows.
By virtue of the statistics $\statistics$,
we attached to every $t$ in $\givenFamily$
a space coordinate $x = S(t)$ in $\statisticsSpace$. 
When $t\sim\familiyDistribution$, $x\sim\pushforwardStat$.
Then, 
the  $\familiyDistribution$-baricentre $\baricentre$
should be the space-time distribution that represent 
the famility $\familiyDistribution$
of time-distributions $t$.
We would like to investiugate to which extent 
slicing $\baricentre$ along the space axes 
allows us 
to recover the $t$'s in $\givenFamily$. 
Let 
$\delta$ 
be a distance on $\probabilitiesOver{\R}$.
For $t$ in $\probabilitiesOver{\R}$,
$\mu$ in $\probabilitiesOver{\R\times\statisticsSpace}$,
and $\epsilon > 0$,
define
\begin{equation*}
D_{\epsilon}(t, \mu)
=
\delta
\left(
\frac
{
\mu\left\lbrace \cdot, B_\epsilon (\statistics(t))\right\rbrace
}
{
\mu\left\lbrace \R,  B_\epsilon (\statistics(t))\right\rbrace
}
,
\,
t
\right)
,
\end{equation*}
where 
$B_\epsilon(\statistics(t))$ 
is the ball centred at $\statistics(t)$ of radius $\epsilon$.
Can we choose a suitable 
$\epsilon$-dependent constant $C_\epsilon$, 
and study the optmisation problem 
\begin{equation}
\label{eq.duality_minimisation}
\inf_{
\mu \in \mathcal{M}
}
\sup_{
\epsilon >0
}
C_\epsilon
\int_{\givenFamily}
D_\epsilon (t, \mu)
\familiyDistribution(dt),
\end{equation}
where 
$\mathcal{M}$ is either 
$\probabilitiesOver{\R\times\statisticsSpace}$
or
$\mathcal{P}_{\pushforwardStat}$
?
How does 
the minimisation problem 
in equation \eqref{eq.duality_minimisation}
relate to
the minimisation of $F$ 
in equation \eqref{eq.baricentre_minimisation}?




